\sysfull

### 2018-04-16 paper/evaluation.tex
Eval revised and enhanced

\begin{wrapfigure}{t!}{0.5\textwidth}
%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP to RF generator antenna distances \{0.15, 0.3, 0.5\}\,m (left, center and right-most bar per application, respectively), compared against Alpaca (results normalized) for ETA coalescing strategy. Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys performs worse than Alpaca \todo{state why it is sometimes worse}{Carlo}}
	\label{fig:runtime}
%\end{figure}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP-to-exciter distances \{0.15, 0.3, 0.5\}\,m, compared against Alpaca (results normalized to Alpaca's performances) for ETA coalescing strategy. Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys is comparable with, or worse than, Alpaca.
	\label{fig:runtime}
%\end{figure}
\end{wrapfigure}
